### 2015-07-09 2015-compmorphon-morphver/poster.tex
Fran's typo
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61237 72bbbca6-d526-0410-a7d9-f06f51895060
more Fran-os
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61238 72bbbca6-d526-0410-a7d9-f06f51895060
more minor fixes to future work
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61239 72bbbca6-d526-0410-a7d9-f06f51895060
more typoes agh
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61240 72bbbca6-d526-0410-a7d9-f06f51895060
typoooooes
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@6124

			\scalebox{0.83}{
				\begin{tabular}{lllll}
					\toprule
					\textbf{Type} & \textbf{Gloss} & {\small \texttt{\tag{adj}(\tag{comp})}} & {\small \texttt{\tag{adj}(\tag{comp})\tag{subst}}} & {\small \texttt{\tag{adj}(\tag{comp})\tag{advl}}} \\
					\midrule
					\textbf{A1} & \eng{good} & {\qipa яхшы (яхшырак)} & {\qipa яхшы (яхшырак)} & {\qipa яхшы (яхшырак)} \\
					\textbf{A2} & \eng{old} & {\qipa иске (искерәк)} & {\qipa иске (искерәк)} & {\qipa — (—)} \\
					\textbf{A3} & \eng{dead} & {\qipa үле (—)} & {\qipa үле (—)} & {\qipa — (—)} \\
					\textbf{A4} & \eng{basic} & {\qipa төп (—)} & {\qipa — (—)} & {\qipa — (—)} \\
					\bottomrule
				\end{tabular}
			}\\
			\begin{itemize}
				%\item Interestingly, native-speaker intuitions on the morphological limitations of a given adjective can often be more restrictive than the range of possible uses found in a large text corpus.
				\item Native speaker intuitions on morph.\ limitations often more restrictive than range of possible uses found in large text copora.
			\end{itemize}
	}

@@

		\headerbox{Ongoing and future work}{name=nedostatki,column=2,below=tuvanvelars}{
		\begin{itemize}
				\item Current annotation of a dependency treebank for Kazakh:\\
				a similar process that helps identify errors in morphological analyses and automatic disambiguation (constraint grammar)
				%\item Leading to
				\begin{itemize}
					\item Improved rule-based morphological disambiguation% (constraint grammar)
					\item Improved morphological analyser for Kazakh
					\item A syntactic depedency treebank for Kazakh
				\end{itemize}
				%\item Work on rule-based morphological disambiguation with constraint grammar
				\item Future work
				\begin{itemize}
					\item Annotate more gold standard text in more Turkic languages
					\item Resaerch cross-lingual techniques for analysing Turkic
				\end{itemize}
				%\item Disambiguation, more stems, clean up transducers
				%\item Machine translation between these languages
				%\item Bring other Kypchak transducers to comparable performance:\\
				%Qaraqalpaq, Bashqort, Nogay, Crimean Tatar
				%\item Other Turkic lgs:\ Uzbek, Uyghur, Chuvash, Yakut, Tuvan, etc.
			\end{itemize}
		}

>>>>

			\scalebox{0.83}{
				\begin{tabular}{lllll}
					\toprule
					\textbf{Type} & \textbf{Gloss} & {\small \texttt{\tag{adj}(\tag{comp})}} & {\small \texttt{\tag{adj}(\tag{comp})\tag{subst}}} & {\small \texttt{\tag{adj}(\tag{comp})\tag{advl}}} \\
					\midrule
					\textbf{A1} & \eng{good} & {\qipa яхшы (яхшырак)} & {\qipa яхшы (яхшырак)} & {\qipa яхшы (яхшырак)} \\
					\textbf{A2} & \eng{old} & {\qipa иске (искерәк)} & {\qipa иске (искерәк)} & {\qipa — (—)} \\
					\textbf{A3} & \eng{dead} & {\qipa үле (—)} & {\qipa үле (—)} & {\qipa — (—)} \\
					\textbf{A4} & \eng{basic} & {\qipa төп (—)} & {\qipa — (—)} & {\qipa — (—)} \\
					\bottomrule
				\end{tabular}
			}\\
			\begin{itemize}
				%\item Interestingly, native-speaker intuitions on the morphological limitations of a given adjective can often be more restrictive than the range of possible uses found in a large text corpus.
				\item Native speaker intuitions on morph.\ limitations often more restrictive than range of possible uses found in large text corpora.
			\end{itemize}
	}

@@

		\headerbox{Ongoing and future work}{name=nedostatki,column=2,below=tuvanvelars}{
		\begin{itemize}
				\item Current annotation of a dependency treebank for Kazakh:\\
				a similar process that helps identify errors in morphological analyses and automatic disambiguation (constraint grammar)
				%\item Leading to
				\begin{itemize}
					\item Improved rule-based morphological disambiguation% (constraint grammar)
					\item Improved morphological analyser %for Kazakh
					\item A syntactic dependency treebank %for Kazakh
				\end{itemize}
				%\item Work on rule-based morphological disambiguation with constraint grammar
				\item Future work:
				\begin{itemize}
					\item Annotate more gold standard text in more Turkic languages
					\item Research cross-linguistic techniques for analysing Turkic
				\end{itemize}
				%\item Disambiguation, more stems, clean up transducers
				%\item Machine translation between these languages
				%\item Bring other Kypchak transducers to comparable performance:\\
				%Qaraqalpaq, Bashqort, Nogay, Crimean Tatar
				%\item Other Turkic lgs:\ Uzbek, Uyghur, Chuvash, Yakut, Tuvan, etc.
			\end{itemize}
		}
